---
title: "LabReport"
output: html_document
date: "2025-04-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("main.R")

```

## Step 3:  Exploring Trends

```{r TIMESERIES, echo=FALSE}
grid.arrange(g_price, g_demand, g_supply, nrow=3)
```


### questions

1. What do you notice about the trends in corn prices?
  - Corn prices seem to be stable before 2005 and then spiked up over the next 10 years before dropping down a bit. It is interesting since supply and demand changes dont seem to be the reason for the price changes. This means that price pressures must be external to the USA or this dataset.
2. How about demand and supply?
  - Demand and supply seem to be steadily rising which makes sense both in terms of population growht as well as steady economic output increase in the USA
3. What was happening around 2006 to cause the price of corn to rise so rapidly during that period?
  - 
4. What can you say from these graphs about the relative sizes of demand and supply over time? Does one tend to outstrip the other?
- They seem to go hand in hand. It seems that corn supply is somewhat larger in terms of raw value (curve would be above the demand)


## Step 4 : Relating Price to Corn Stock-to-Use Ratio
1. (Word Doc) Make a scatter plot of corn prices on the y-axis and the stock-to-use ratio (SUR) on the x-axis with a linear regression line. What is the general relationship between corn prices and the SUR? Is a linear regression line a good representation of this relationship? 

```{r SUR, echo=FALSE}
g_pricevsSUR
```


### Question fomr lab:
1. Does a linear regression line do a good job of fitting the underlying relationship between prices and SUR?
  - It seems so. There are some outliers in terms of corn price at lower SUR values though.
  
## Step 5 : Linear Regression and Diagnostics
2. Run the linear regression: Corn Price_t=α+βSUR_t+ε_t and show the regression output in a table. Include the regression coefficients, their standard errors, and the R-squared value. How do you interpret the coefficient on SUR? Is this consistent with the theory of supply and demand? How do you interpret the R-squared value? Describe the overall fit of this model.

### Estimating the Regression Model
```{r}
reg1_summary
t_reg1_residualSummary
```

### Calculating Price Elasticity

### Question:
1. How responsive (elastic) is the price of corn to changes in corn supply and demand?
  - 
  
  
  
## From word Doc for submission: 





3. Run the non-linear regression: Corn Price_t=α+β(1/(SUR_t ))+ε_t and show the regression output in a table. Include the regression coefficients, their standard errors, and the R-squared value. From this model, what is the marginal effect of SUR on the price of corn? Hint: if y=1/x then dy/dx = -1/x^2.

4. Create a scatter plot of corn prices on SUR with regression lines for two distinct periods: 1973-2005 vs. 2006-2019. How did the relationship change between the two time periods? What could explain this?

5, Run the linear regression with a dummy variable for the post 2006 period and an interaction between the post-2006 dummy and SUR: Corn Price_t=α+βSUR_t+δP2006_t+γ(P2006_t×SUR_t ) 〖+ε〗_t and show the regression output in a table. Include the regression coefficients, their standard errors, and the R-squared value. From this model, what is the marginal effect of SUR on the price of corn in the 1973-2005 period? What is the effect of SUR in the 2006-2019 period? How do you interpret the coefficient on the P2006 dummy variable?  


